Paper 3 - Causal Roadmap

### 2023-03-27 docs/causal_roadmap.qmd
Added DAG for bimoarker to outcome

## Data Checking

@@

## Checklist A: Replicability

@@

## DAGs

@@

### Research question 1: `r rq1.title`

@@

### Research question 2: `r rq2.title`

@@

### Research question 3: `r rq3.title`

>>>>

<!-- ####################################################################### -->
## Data Checking
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
## Checklist A: Replicability
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
## Gene-Environment Interactions
<!-- ####################################################################### -->

Genetic polymorphisms relevant for the **chemicals**:

* \acr{opps}:
  * The \acr{snps} of the *PON1* (paraoxonase 1) gene, known to influence the ability to metabolize and detoxify \acr{opps}: `rs854560` and `rs662`. Reference: https://doi.org/10.1289/ehp.1408976.
  * The \acr{snps} of the genes coding for \acr{opps}-metabolizing enzymes: `rs1803274`, `rs1799807`, `rs662`, `rs854560`, `rs705379`, `rs4244285`, `rs3892097`, and `rs2177180`. Reference: https://doi.org/10.1016/j.chemosphere.2015.07.079.
* Phenols:
  * The \acr{snp} of the *UGT2B15* gene: `rs1902023`. Reference: https://doi.org/10.1016/j.envint.2020.106172.
* Phthalates:
  *  The \acr{snps} of the cytochrome P450 (*CYPs*) and UDP-glucuronosyltransferase (*UGTs*) genes: `rs1057910`, `rs1799853`, `rs4244285`, `rs12248560`, `rs3892097`, `rs1902023`, and `rs11692021`. Reference: https://doi.org/10.1016/j.envint.2021.107046.
  * The \acr{snps} of the *PPAR*$\alpha$ gene: `rs75525202`, `rs4823902`, `rs4253690`, `rs12330015`, `rs5766698`, `rs115250492`, and `rs1800246.` Reference: https://doi.org/10.3389/fgene.2022.855544. Not sure whether these \acr{snps} should be considered in the list below.

Genetic polymorphisms relevant for the **outcomes**:

<!-- ####################################################################### -->
## DAGs
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
### Research question 1: `r rq1.title`
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
### Research question 2: `r rq2.title`
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
### Research question 3: `r rq3.title`
<!-- ####################################################################### -->
